I can see clearly now: reinterpreting statistical significance

### 2018-10-09 doc.tex
GoodBook chapter ref

The value of NHST can be seen in something like a permutation-based t-test \cite{GoodBook}: it provides a simple, robust framework to ask whether we can tell \emph{which} mean is bigger. 
More generally, testing the null hypothesis is a proxy for asking whether we clearly see a signal of how our data differs from it.
In many cases, this comes down simply to whether we can be confident of the \emph{sign} of a difference or a correlation coefficient \citep{robinson2001past}. 
In other cases (e.g., multi-way ANOVA), it may not be simple to describe the difference, but NHST is still a reasonable, accepted way to evaluate whether something has been seen clearly.

>>>>

The value of NHST can be seen in something like a permutation-based t-test \cite[Chapter 1]{GoodBook}: it provides a simple, robust framework to ask whether we can tell \emph{which} mean is bigger. 
More generally, testing the null hypothesis is a proxy for asking whether we clearly see a signal of how our data differs from it.
In many cases, this comes down simply to whether we can be confident of the \emph{sign} of a difference or a correlation coefficient \citep{robinson2001past}. 
In other cases (e.g., multi-way ANOVA), it may not be simple to describe the difference, but NHST is still a reasonable, accepted way to evaluate whether something has been seen clearly.
